---
title: "Midterm Exam Review"
author: "Adam Kaderbhai"
format: pdf
---

# 1.)
Compute the following in $N(2.0, 0.3^2)$, the normal distribution with mean 2.0
and standard deviation 0.3.
(a) P(X < 2.5)
(b) P(X > 2.1)
(c) P(1.6 ≤ X ≤ 2.0)
(d) Find the value c so that P(X ≤ c) = .25
```{r}
pnorm(2.5, 2.0, 0.3)
1 - pnorm(2.1, 2.0, 0.3)
pnorm(2.0, 2.0, 0.3) - pnorm(1.6, 2.0, 0.3)
qnorm(.25, 2.0, .3)
```

# 2.) 
In a survey, 1600 adults were asked how many cups of coffee they drink per 
day. The results are given below.

Cups per day  0     1     2     3     4     5
Frequency     570   432   299   152   112   35

If a random person is selected from the group, the expected value is µX =
1.32 and the standard deviation is σX = 1.34, as we computed earlier in the
semester.
(a) Describe the distribution of X, the random variable obtained by taking the
mean of a sample of size n = 25 from this distribution.
```{r}
1.34/sqrt(25)
```


(b) What is the probability that X is at least 1.5?
```{r}
pnorm(1.5, 1.32, 1.34 )
```

(c) What is the probability that X is between 1 and 2?
```{r}
pnorm(2, 1.32, 1.34) - pnorm(1, 1.32, 1.34)
```
3. The Union Shield Penny (one of two pennies currently minted in the U.S.) has
a mean weight of 3.11 grams with a standard deviation of .03g. These weights
are normally distributed.

(a) What is the probability that a randomly selected penny has weight less
than 3.15g?

(b) What is the probability that a randomly selected penny has weight greater
than 3.12g?

(c) What is the probability that a randomly selected penny has weight between
3.10 and 3.13g?

(d) A certain penny weighs less than 60% of pennes. What is its weight?

(e) What is the z-score of such a penny? Interpret this number is words.

(f) What is the probability that 10 randomly selected pennies have average
weight greater than 3.13g?

(g) What is the probability that a roll of 50 pennies weighs more than 155.2g?
```{r}
pnorm(3.15, 3.11, .03)

1 - pnorm(3.12, 3.11, .03)

pnorm(3.13, 3.11, .03) - pnorm(3.10, 3.11, .03)

qnorm(.60, 3.11, .03)

Z_Score = (qnorm(.60, 3.11, .03) - 3.11) / .03

1 - pnorm(3.13, 3.11, .03/sqrt(10))


```
Problem 6

```{r}
library(readxl)
freshman_15 <- read_excel("freshman_15.xlsx")
View(freshman_15)
```

```{r}
mean(freshman_15$WT_SEPT)

```



