---
title: "Take Home Midterm 3"
author: "Adam Kaderbhai"
format: pdf
---

```{r}
#| echo: false
library(readxl)
optical <- read_excel("optical.xlsx")
```

# Problem 6

This problem refers to the optical data set, available on Moodle. This set represents a random
sample of 43 patients at an optometry clinic. In this problem, we are interested in the eye difference
variable. Positive values indicate greater weakness in the left eye.

## (a) 
Construct a level 90% confidence interval for eye difference in the population from which this
sample was drawn using direct calculation. Identify the point estimate, margin of error, and
interval endpoints. Make sure your work is clear.

```{r}
point_estimate <- mean(optical$eye_difference)
point_estimate

standard_dev <- sd(optical$eye_difference)

n <- 43

C_level <- qt(.95, df = 42)

Margin_of_Error <- C_level * (standard_dev/sqrt(n))
Margin_of_Error

point_estimate - Margin_of_Error
point_estimate + Margin_of_Error
```

- The point estimate is the sample mean which is equal to -0.38
- The Margin of Error is 0.43
- interval end point (-0.81, 0.04)


## (b) 
Confirm the results of part (a) with a single line of R code. Include both code and output.

```{r}
t.test(optical$eye_difference, conf.level = 0.90)
```
\newpage

## (c) 
Write a sentence or two interpreting your result using the language from class. Your answer
should say something about which eye, if either, tends to require greater correction.



- With 90% Confidence Interval the mean eye difference for the population is between -0.81 to 0.04.

- In this sample the right eye tends to require more correction in the sample (sample mean = −0.38).

- If the population mean were 0 which is in the range (-0.81, 0.04), then there would be ambiguity about which eye needs more correction.







