---
title: "HW 11.18"
author: "Adam Kaderbhai"
format: pdf
---



# Problem 1
A medical school advertises that the mean starting salary of its graduates is $89,000. Concerned that it may actually
be less, a group of first-years surveys 38 recent graduates, finding a sample mean of $85,500. Assume $σ$= $8000.




## a.)
- $H_o$ : The mean starting salary of the graduates is $89,000
- $H_a$ : The mean starting salary of the graduates is less than $89,000


## b.)
```{r}
(85500 - 89000) / (8000/sqrt(38))
```

## c.)
```{r}
pnorm(85500, 89000,8000/sqrt(38))
```

## d.)
since the p-value = 0.0035 is less than $α$ the result is statistically significant.

## e.)
Based on the survey data, there is strong statistical evidence to suggest that the true mean starting salary for graduates of the medical school is less than the advertised $89,000. The probability of observing a sample mean of $85,500 or lower purely by random chance (if the true mean were $89,000) is very low (only about 0.35%). Therefore, the first-year students' concern appears to be justified.
