---
title: "HW11.10"
author: "Adam Kaderbhai"
format: pdf
---


# Problem 1
In a simple random sample of 10 sales clerks at convenience stores in 1989, the mean salary was $25,352.87 and
the standard deviation was $3,202.09. Compute a level 95% confidence interval for the population mean. Carefully
justify your answer.

```{r}
Conf_lvl <- qt(0.975, 9)

Conf_lvl*(3202.09/sqrt(10))

```
The t-distribution is used because the population standard deviation is unknown and must be estimated from the sample. This method is appropriate for the small sample size (n=10) as it accounts for the additional uncertainty that comes from using a sample to estimate the population parameters. This requires the assumption that the underlying population of salaries is approximately normally distributed.

\newpage

# Problem 2
Using the R data set mtcars, construct a level 90% confidence interval for the mean horsepower of all cars (a) by
direct computation and (b) using the t.test function. Confirm that your answers agree with one another.

## a.)
```{r}
mean_hp <- mean(mtcars$hp)
sd_hp <- sd(mtcars$hp)

Conflvl_hp <- qt(0.95, 31)

mu = Conflvl_hp * (sd_hp/sqrt(32))

mean_hp - mu
mean_hp + mu

```

## b.)
```{r}
t.test(mtcars$hp, conf.level = .90)
```

## c.)
Both results yield the exact same intervals
