---
title: "HW 11.5"
author: "Adam Kaderbhai"
format: pdf
---
```{r}
library(readxl)
```

- Increasing C increases the margin of error E.
- Increasing σ increases the margin of error E.
- Increasing n decreases the margin of error E.

# Problem 1

```{r}
1.645 * (72.50/sqrt(55))
```

# Problem 2
```{r}
1.645 * (72.50/sqrt(85))
```
The one with sample size n = 85 is lower because the population size(n) and Margin of Error(E) are inversely proportional

\newpage
# Problem 3
```{r}
1.960 * (1.04/sqrt(282))
```

# Problem 4
```{r}
1.960 * (1.92/sqrt(282))
```
E is higher because σ and E are direcrly proportional

# Problem 5
```{r}
mileage <- read_excel("mileage.xlsx")
mean(mileage$mpg)

1.960 * (3.5/sqrt(45))
```

# Problem 6
```{r}
2.576 * (3.5/sqrt(45))
```
 E is higher because `C` and `E` are directly proportional
 
# Problem 7

```{r}
((1.960 * 25)/15)^2
```
n = 11

# Problem 8
```{r}
((1.960 * 25)/5)^2
```
n = 97

# Problem 9
Sample size always increases with larger σ. If σ increases, the required sample size increases in both problems to maintain the same confidence and margin of error.

# Problem 10
SIMILARITIES:

- Both are symmetric (bell-shaped curves)

- As the degrees of freedom increase (or as the sample size n grows large), the t-distribution approaches the standard normal distribution (z-distribution).

- Both are used for calculating confidence intervals.

DIFFERENCES:

- The t-distribution is more spread out than the standard normal.

- The shape of the t-distribution changes with degrees of freedom, while the standard normal is fixed.

- Use the  (z-distribution) when σ is known and n is large while.

- Use the t-distribution when σ is unknown or when n is small.

