---
title: "HW9.23"
author: "Adam Kaderbhai"
format: pdf
---

```{r}
#| message: false
library(tidyverse)
```


The Z- score formula is 
$$ Z = \frac{x - \mu}{\sigma} $$ 


# Problem 1

A certain kids’ fun run has two age categories: 8-11 and 12-14. Finishing times in the younger group have mean
33 minutes and standard deviation 4 minutes, while finishing times in the older group have mean 29 minutes and
standard deviation 5 minutes.
- (a) Find and interpret the z-score of an 8-11 year old who finishes in 24 minutes.
- (b) Find and interpret the z-score of a 12-14 year old who finishes in 24 minutes.
- (c) Which is the more unusual of these two?


finishing times 8 - 11 
$$\mu = 33 $$ 
$$ \sigma = 4 $$
finishing times 12 - 14 
$$\mu = 29 $$ 
$$ \sigma = 5 $$


### a.) 

```{r}
(24 - 35)/4
```
### b.)

```{r}
(24 - 29)/5
```

### c.)

Z-Score of 8 - 11 year olds = -2.75
Z-Score of 12 - 14 year olds = -1.00

The Z-Score of -2.75 is more unusual

# Problem 2

```{r}
glimpse(faithful)
```

```{r}
mean(faithful$eruptions)
sd(faithful$eruptions)
```
```{r}
(5 - 3.487783)/1.141371
```
The Z-Score of 5 minute eruption is 1.324913 mins above the mean

# Problem 3

A music streaming app determines that users’ daily usage is approximately bell shaped with mean 55 minutes and
standard deviation 14 minutes. Fill in the blanks:

- Approximately 68% of users listen between 41 and 69 mins
- Approximately 95% of users listen between 27 and 83 mins
- Approximately 99.7% of users listen between 13 and 97 mins

# Problem 4

Cholesterol levels for women aged 20-34 are normally distributed (bell-shaped) with mean 185 mg/dl. Approximately
95% of women in this age group have cholesterol between 127 and 243. What is the standard deviation of this
distribution? 

So the Z-Score of such observation is 2 

- 185 - 2x = 127
- 185 + 2x = 243

```{r}
(185 - 127)/2
(243-185)/2
```
The Standard Deviation is 29

